Check Coverage

### 2020-09-07 analysis/merge_data.Rmd
Get rid of duplicates

comp_biotime_traits <- map_dfr(traits, merge_data) %>%
  right_join(biotime_data %>% select(-sourceName, -scientificName))

@@

usethis::use_data(study_table)
```

>>>>

comp_biotime_traits <- map_dfr(traits, merge_data) %>%
  right_join(biotime_data %>% select(-sourceName, -scientificName)) %>%
  distinct()

@@

usethis::use_data(study_table)
pins::pin(study_table, board = "github")
```
